### 2012-03-16 docs/runtime_parameters/runtime_parameters.tex
update

\rowcolor{tableShade}
\verb=  small_dens  = &    &  1.d-5 \\
\verb=  small_temp  = &    &  5.d6 \\
\rowcolor{tableShade}
\verb=  use_eos_coulomb  = &   use the Coulomb corrections between ions (if supported by the EOS)  &  .true. \\

@@

>>>>

\rowcolor{tableShade}
\verb=  small_dens  = &    &  1.d-5 \\
\verb=  small_temp  = &    &  5.d6 \\
\rowcolor{tableShade}
\verb=  use_eos_coulomb  = &   use the Coulomb corrections between ions (if supported by the EOS)  &  .true. \\
\verb=  use_eos_e_instead_of_h  = &   In deriving the temperature from the $h$, first subtract off $p_0/\rho$ to define $e$, and use that as the input to the EOS.  &  .false. \\

@@

\verb=  xhi_boundary_type  = &   $+x$ boundary condition name---if this is set, it overrides the integer value set through {\tt bcx\_hi}  &  "" \\
\verb=  xlo_boundary_type  = &   $-x$ boundary condition name---if this is set, it overrides the integer value set through {\tt bcx\_lo}  &  "" \\
\verb=  yhi_boundary_type  = &   $+y$ boundary condition name---if this is set, it overrides the integer value set through {\tt bcy\_hi}  &  "" \\
\verb=  ylo_boundary_type  = &   $-y$ boundary condition name---if this is set, it overrides the integer value set through {\tt bcy\_lo}  &  "" \\
\verb=  zhi_boundary_type  = &   $+z$ boundary condition name---if this is set, it overrides the integer value set through {\tt bcz\_hi}  &  "" \\
\verb=  zlo_boundary_type  = &   $-z$ boundary condition name---if this is set, it overrides the integer value set through {\tt bcz\_lo}  &  "" \\
